\begin{thebibliography}{99}
\singlespace \normalsize


\bibitem{alves}
  ALVES, I.R. Making your life easier with domain-specific languages (DSLs).
  In: \emph{WAES}, January 2023.
  [online]. [accessed 06.03.2023]. Available
  \url{https://medium.com/wearewaes/making-your-life-easier-with-domain-specific-languages-dsl-1838d351d35}.

\bibitem{mernik}
  MERNIK, M., HEERING, J., SLOANE, A.M. When and how to develop domain-specific languages.
  In: \emph{ACM Computing Surveys}, December 2005, p. 1
  \url{https://dl.acm.org/doi/10.1145/1118890.1118892}

\bibitem{jetbrains}
  JetBrains. Domain-Specific Languages.
  [online]. [accessed 06.03.2023].
  Accessed October 14, 2022. Available:
  \url{https://www.jetbrains.com/mps/concepts/domain-specific-languages/}.

\bibitem{health}
  Euro Health Observatory (WHO).
  Health and economy.
  [online] [accessed 12.02.2023]. Available:
  \url{https://eurohealthobservatory.who.int/themes/observatory-programmes/health-and-economy}.

\bibitem{country}
  Euro Health Observatory (WHO).
  Country overview. 
  [online]. [accessed 12.02.2023]. Available:
  \url{https://eurohealthobservatory.who.int/countries/republic-of-moldova}.

\bibitem{carp}
  CARP, M.,GOMA, L. Efficiency of medical services in the Republic of Moldova.
  In: \emph{Cercetarea în biomedicină și sănătate: calitate, excelență și performanță. }
  (R), october 20-22, 2021, Chişinău. Chișinău, Republica Moldova: 2021, p. 64.
  \url{https://www.chicagomanualofstyle.org/tools_citationguide/citation-guide-2.html}.

 \bibitem{github}
  Team 11, FAF-212.
  \emph{DSL for analyzing medical results.}
  \url{https://github.com/FAF-UTM/11_FAF_212.git}. 
  
% References 
%1.	ALVES, I.R. Making your life easier with domain-specific languages (DSLs). In: WAES, January 2023. [online]. [accessed 06.03.2023]. Available: https://medium.com/wearewaes/making-your-life-easier-with-domain-specific-languages-dsl-1838d351d35
%2.	MERNIK, M., HEERING, J., SLOANE, A.M. When and how to develop domain-specific languages. In: ACM Computing Surveys, December 2005, p. 1 https://dl.acm.org/doi/10.1145/1118890.1118892
%3.	JetBrains. Domain-Specific Languages. [online]. [accessed 06.03.2023].
% Available: https://www.jetbrains.com/mps/concepts/domain-specific-languages/
%4.	Euro Health Observatory (WHO). Health and economy. [online] [accessed 12.02.2023]. Available: https://eurohealthobservatory.who.int/themes/observatory-programmes/health-and-economy

%5.	Euro Health Observatory (WHO). Country overview. [online]. [accessed 12.02.2023]. Available: https://eurohealthobservatory.who.int/countries/republic-of-moldova

%6.	CARP, M.,GOMA, L. Efficiency of medical services in the Republic of Moldova. In: Cercetarea în biomedicină și sănătate: calitate, excelență și performanță. (R), october 20-22, 2021, Chişinău. Chișinău, Republica Moldova: 2021, p. 64. https://ibn.idsi.md/vizualizare_articol/144098#

\end{thebibliography}

